Security Properties for Stack Safety

### 2021-05-11 short/main.tex
Fixed build issue, added makefile
Polishing on short version

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
%\acmJournal{PACMPL}
%\acmVolume{1}
%\acmNumber{OOPSLA} % CONF = POPL or ICFP or OOPSLA
%\acmArticle{1}
%\acmYear{2021}
%\acmMonth{1}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}

@@

We find that Roessler and Dehon's {\em Depth Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the identity of
the function activation that owns the frame and access to those locations is
then permitted only when that activation is currently executing, validates our
stepwise properties. On the other hand, we reason that \emph{Lazy Tagging and Clearing}
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that \emph{should} enforce
confidentiality, albeit at some performance cost.

>>>>

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{OOPSLA} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2021}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

Our testing supports the stack-safety claim of Roessler and Dehon's {\em Depth
  Isolation} micro-policy, in
which memory cells within each stack frame are tagged with the identity of
the function activation that owns the frame and access to those locations is
then permitted only when that activation is currently executing. On the other hand, we find that their \emph{Lazy
  Tagging and Clearing} policy
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that does enforce
confidentiality (and test that it does), albeit at some performance cost.
